Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-27 conclusion.tex
[draft] iid expanded; 3rd paragraph of section conclusion section modified.

We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The study of the Loschmidt echo is a generalization of the conventional ``cut-and-join" protocol. Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient. Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices and depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$s.

>>>>

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$. Generic value of $\theta$ then interpolates those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface, which we denote as
\begin{equation}
S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

### 2017-06-27 num_result.tex
[draft] iid expanded; 3rd paragraph of section conclusion section modified.

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming iid Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

>>>>

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.
